Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-11-30 doc/manuscript/translocation.qmd
Update text to account for viability model changes

Given observed yearly adult survival probabilities (from analysis of CMR data) and a yearly survival probability of the year 1 juvenile class ($\sigma_{J_1}$) greater than 0.09, at least six of twelve translocated populations should experience a long-run growth rate $\lambda$ greater than 1 in the presence of Bd (@fig-viability A; median predicted $\lambda$ ranges from 1.XX-1.XX for these six populations).
These six populations all had observed yearly adult survival greater than 0.5.
As year 1 juvenile survival probability increased above 0.2, the deterministic long-run growth rate of eight of twelve population was greater than 1 (@fig-viability A).

Even when incorporating (i) demographic stochasticity and (ii) environmental stochasticity in juvenile survival and recruitment (for year 1 and year 2 juveniles, the transition that we expect to be the most subject to environmental variability in the presence of Bd), populations with high adult survival are likely to persist over a 50 year time horizon.
Our model predicted that, following a single introduction of 40 adult individuals into a population, the six populations with the highest adult survival probabilities ($\sigma_{A_R} > 0.5$) had 50-year extinction probabilities of less than 0.5 when the average percent reduction in juvenile survival was less than 50% (given baseline year 1 juvenile survival probability of 0.25; @fig-viability B).
This indicates strong potential for long-term persistence in the presence of Bd and environmental variability in survival and recruitment.
When we decreased baseline year 1 juvenile survival to 0.09, 50-year extinction probability was of less than 50% for four of these populations (X-X) and greater than 50% (X-X) for two of these populations (@fig-viability B).
In contrast, for the six populations where yearly adult survival probability $\sigma_{A_R} < 0.5$, extinction probability over 50 years was always predicted to be \>50% regardless of baseline year 1 survival probability.
To test the validity of our model predictions, we demonstrated that our stochastic model could describe the general recovery trajectory of our translocated population with the longest survey history (@fig-viability C; population 70550, surveyed for 16 years).

@@

Reintroduction of resistant/tolerant MYL frogs was remarkably successful in reestablishing viable populations in the presence of Bd.
Of the 12 translocated populations, approximately 80% showed evidence of both successful reproduction and recruitment of new adults.
Bd loads measured before and after translocation were similar and generally remained well below the level at which frog mortality occurs.
Annual survival for 12 of the 24 translocated cohorts exceeded 50%, and \> 70% of translocated cohorts had survival above this 50% level when the earliest translocations are excluded (i.e., translocations conducted when methods were still being refined).
The fact that the relatively low Bd loads and correspondingly high frog survival in the presence of Bd was maintained between the natal/donor sites and the recipient sites indicates that these characteristics of naturally-recovering populations were not solely an effect of the natal/donor site or site \* frog interactions, but instead were due at least in part to resistance/tolerance inherent in the frogs.
In addition, the relatively high survival of translocated frogs was maintained in their progeny, as expected if resistance/tolerance has a genetic basis.
Results from the population viability model were also encouraging.
In particular, translocated populations with \> 50% survival in the first year post-translocation were predicted to have a low probability of extinction over 50 years (probability of extinction = 0 - 0.32).
In light of the generally low success rate of amphibian reintroduction efforts [@dodd2005], our success in reestablishing MYL frog populations via translocation of resistant/tolerant individuals is striking, and even more so given that this success occurred despite ongoing infection of frogs with Bd.

@@

$$
\begin{bmatrix}
L_1 \\
L_2 \\
L_3 \\
J_1 \\
J_2 \\
A_R \\ 
A_T
\end{bmatrix}(t + 1) = 
\begin{bmatrix}
  0 & 0 & 0 & 0 & 0 & \sigma_{A_R} p_F F & \sigma_{A_T} p_F F \\
  \sigma_{L1} p_{L1} & 0 & 0 & 0 & 0 & 0 & 0 \\
  0 & \sigma_{L2} p_{L2} & 0 & 0 & 0 & 0 & 0\\
  \sigma_{L1} (1 - p_{L1}) & \sigma_{L2} (1 - p_{L2}) & \sigma_{L3} & 0 & 0 & 0 & 0 \\
  0 & 0 & 0 & \sigma_{J1} p_{J1}(1 - \omega) & 0 & 0 & 0 \\
  0 & 0 & 0 & \sigma_{J1} (1 - p_{J1}) (1 - \omega) & \sigma_{J2} (1 - \omega) & \sigma_{A_R} & 0 \\
  0 & 0 & 0 & 0 & 0 & 0 & \sigma_{A_T} 
\end{bmatrix} \begin{bmatrix}
L_1 \\
L_2 \\
L_3 \\
J_1 \\
J_2 \\
A_R \\
A_T \\
\end{bmatrix}(t) 
$$

The parameters in this model are yearly survival probability $\sigma_{\cdot}$ (the subscript "$\cdot$" indicates a particular state variable), probability that a female frog reproduces in a given year $p_F$, number of eggs produced by a female frog in a year that successfully hatch $F$, probability of a first-year tadpole remaining as a tadpole $p_{L1}$, probability of a second-year tadpole remaining as a tadpole $p_{L2}$, and probability of a first-year juvenile remaining as a juvenile \$p\_{J1}\$.
The parameter $(1 - \omega)$ gives the percent reduction in baseline juvenile survival and recruitment due environmental stochasticity.

@@

After parameterizing our model with CMR-estimated adult frog survival probabilities and other known vital rates ([@tbl-param_values]), we performed four analyses.
First, we compute the long-run growth rate $\lambda$ for each of our 12 translocated populations to determine if the populations were deterministically predicted to grow or decline in the long-run.
Second, we compute the elasticity of $\lambda$ to model parameters, to quantify how much changes in adult survival, for example, affected the long-run growth rate.
Third, we included demographic and environmental stochasticity in our model and simulated the 50-year viability (i.e., 1 - extinction probability) of populations given an introduction of 40 adult individuals into an unoccupied habitat.
Finally, we fit our model to our longest translocation trajectory to confirm that our model could reasonably reproduce the observed recovery trajectories of MYL frogs following reintroductions.
Additional details are provided in the SI Appendix.
Code to replicate the analyses can be found at <https://github.com/SNARL1/translocation>.

@@

![Population viability analysis of translocated MYL frogs quantified the long-run growth rate and extinction probability of frog populations: (A) Predicted long-run growth rate $\lambda$ for different values of yearly adult survival probability $\sigma_{A_R}$ and probability of recruitment $\omega$, given the parameterized, deterministic model. Colored points show the predicted $\lambda$ values for the twelve translocated populations when probability of recruitment into the adult class is $\omega = 0.3$ (indicated by the dashed line). The red line shows where $\lambda = 1$. Note that the point for 70413 is mostly hidden behind other points. (B) Predicted 50-year extinction probabilities of the 12 translocated populations, given demographic stochasticity, environmental variability in $\omega$, and different mean values of $\omega$. The dashed line shows where $\omega = 0.3$, for comparison to (A). There are 6 lines at extinction probability = 1, 5 of which (70414--70619) are hidden beneath the line for 70505. (C) 100 simulated trajectories (black lines) from the population viability model that most closely matched the observed abundance trajectory of adult amphibians at site 70550 (light orange).](figures/pop_viability_figures_for_manuscript.jpg){#fig-viability width="600"}

@@

We extracted yearly survival probabilities for translocated adults $\sigma_{A_T}$ and naturally recruited adults $\sigma_{A_R}$ from the CMR model used to estimate population-level parameters of translocated populations (see "Materials and Methods - Estimation of frog survival and abundance" in main paper).
Although we observed yearly variability in adult survival within a population, the magnitude of this variability was small compared to among-population variability ([@fig-translocation-survival]).
Thus, we did not include yearly within-population variability in adult survival in this analysis.
However, within a population there was substantial yearly variability in the successful recruitment of adults, greater than what we would expect from Poisson variability around a mean value.
Therefore, we allowed for yearly variability in the probability of successful recruitment $\omega$ (additional details provided in "Estimating model parameters" below).

@@

We performed four analyses on our model.
First, we considered a deterministic version of our model with no yearly heterogeneity in probability of successful recruitment $\omega$, and calculated the predicted long-run growth rate $\lambda$ of a population for different values of $\sigma_{A_R}$ and $\omega$.
We then fixed $\omega = 0.3$ and calculated the predicted growth rate of our 12 populations.

Second, we performed a local elasticity analysis on $\lambda$ with respect to parameters $\omega$, $\sigma_{A_R}$, and $F$ to determine how small changes in these parameters could influence the long-run deterministic growth rate of populations (@fig-viability-supp).

Third, we defined a version of the model with demographic and environmental stochasticity, where environmental stochasticity was represented by among-year variability in $\omega$.
We used this model to simulate a one-time introduction of 40 translocated adult frogs.
We ran this simulation 1000 times for each population and computed the probability of a population becoming extinct after 50 years given the observed parameter values and environmental stochasticity in $\omega$.
We varied the mean recruitment probability $\omega$ from 0.15 and 0.4 and drew values of $\omega$ each year from a beta distribution with a dispersion parameter of $\phi = 2$ (when $\omega = 0.5$ and $\phi = 2$ the beta distribution is uniform between 0 and 1).

Finally, we assessed whether our stochastic model could reproduce observed trajectories of population recovery.
We focused on population 70550 because this was our longest CMR time series for a translocated population and because this population shows evidence of substantial post-translocation increases in adult abundance associated with population establishment and recovery.
We simulated our model for 16 years, repeating the simulation 50,000 times.
For each run and each year, we drew $\omega$ from a uniform distribution between 0 and 1 (or equivalently a beta distribution with mean 0.5 and $\phi = 2$).
Using Approximate Bayesian Computing and rejection sampling [@kosmala2016], we identified the top 2% of trajectories (i.e., 1000 trajectories) that minimized the sum of squared errors between the observed and predicted data.
The $\omega$ values associated with these "best" trajectories represented an approximate posterior distribution [@beaumont2010].
Using these best fit trajectories, we assessed whether our model could qualitatively describe the patterns of recovery in the observed data for population 70550.

@@

![Sensitivity analysis of the stage-structured MYL frog model. Elasticity of $\lambda$ with changes in 3 parameters: $\sigma_{A_R}$ (yearly survival probability of naturally recruited adults), $\omega$ (yearly probability of successful recruitment from juveniles to adults), and *F (*number of eggs produced by a female frog in a year that successfully hatch). Elasticity is calculated at the default parameter values for each population and $\omega$ = 0.3.](figures/pop_viability_figures_for_supp.jpg){#fig-viability-supp width="450"}

@@

| **Parameter**                                                             | **Value**            | **Source**                                                         |
|:----------------------------|:-----------------|:-------------------------|
| $\sigma_{L_1}$, Yearly survival probability of year 1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{L_2}$, Yearly survival probability of year 2 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{L_3}$, Yearly survival probability of year 3 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{J_1}$, Yearly survival probability of year 1 juveniles           | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $\sigma_{J_2}$, Yearly survival probability of year 2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from mark-recapture studies                              |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from mark-recapture studies                              |
| $p_{L_1}$, Probability of a year 1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations, natural history knowledge |
| $p_{L_2}$, Probability of a year 2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $p_{J_1}$, Probability of a year 1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, natural history knowledge |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                 |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                 |
| $\omega$, Probability of juvenile successfully recruiting to an adult     | Varies yearly        | Explored different values of this parameter                        |

>>>>

Given observed yearly adult survival probabilities (from analysis of CMR data) and a yearly survival probability of the year 1 juvenile class ($\sigma_{J_1}$) greater than 0.09, at least six of twelve translocated populations should experience a long-run growth rate $\lambda$ greater than 1 in the presence of Bd (@fig-viability A; median predicted $\lambda$ ranges from 1.19-1.40 for these six populations).
These six populations all had observed yearly adult survival greater than 0.5.
As year 1 juvenile survival probability increased above 0.2, the deterministic long-run growth rate of eight of twelve population was greater than 1 (@fig-viability A).

Even when incorporating (i) demographic stochasticity and (ii) environmental stochasticity in year 1 juvenile survival and recruitment (the transition that we expect to be the most subject to environmental variability in the presence of Bd), populations with high adult survival are likely to persist over a 50 year time horizon.
Our model predicted that, following a single introduction of 40 adult individuals into a population, the six populations with the highest adult survival probabilities ($\sigma_{A_R} > 0.5$) had 50-year extinction probabilities of less than 0.5 when the average year 1 juvenile survival was greater than 0.10 (@fig-viability B).
This indicates strong potential for long-term persistence in the presence of Bd and environmental variability in survival and recruitment.
In contrast, for the six populations where yearly adult survival probability $\sigma_{A_R} < 0.5$, extinction probability over 50 years was always predicted to be \>50% regardless of the value of mean year 1 juvenile survival between 0 - 0.25.
To test the validity of our model predictions, we demonstrated that our stochastic model could describe the general recovery trajectory of our translocated population with the longest survey history (@fig-viability C; population 70550, surveyed for 16 years).

@@

Reintroduction of resistant/tolerant MYL frogs was remarkably successful in reestablishing viable populations in the presence of Bd.
Of the 12 translocated populations, approximately 80% showed evidence of both successful reproduction and recruitment of new adults.
Bd loads measured before and after translocation were similar and generally remained well below the level at which frog mortality occurs.
Annual survival for 12 of the 24 translocated cohorts exceeded 50%, and \> 70% of translocated cohorts had survival above this 50% level when the earliest translocations are excluded (i.e., translocations conducted when methods were still being refined).
The fact that the relatively low Bd loads and correspondingly high frog survival in the presence of Bd was maintained between the natal/donor sites and the recipient sites indicates that these characteristics of naturally-recovering populations were not solely an effect of the natal/donor site or site \* frog interactions, but instead were due at least in part to resistance/tolerance inherent in the frogs.
In addition, the relatively high survival of translocated frogs was maintained in their progeny, as expected if resistance/tolerance has a genetic basis.
Results from the population viability model were also encouraging.
In particular, translocated populations with \> 50% survival in the first year post-translocation were predicted to have a low probability of extinction over 50 years (probability of extinction $<$ 0.5 when year 1 juvenile survival probability was greater than 0.10).
In light of the generally low success rate of amphibian reintroduction efforts [@dodd2005], our success in reestablishing MYL frog populations via translocation of resistant/tolerant individuals is striking, and even more so given that this success occurred despite ongoing infection of frogs with Bd.

@@

$$
\begin{bmatrix}
L_1 \\
L_2 \\
L_3 \\
J_1 \\
J_2 \\
A_R \\ 
A_T
\end{bmatrix}(t + 1) = 
\begin{bmatrix}
  0 & 0 & 0 & 0 & 0 & \sigma_{A_R} p_F F & \sigma_{A_T} p_F F \\
  \sigma_{L1} p_{L1} & 0 & 0 & 0 & 0 & 0 & 0 \\
  0 & \sigma_{L2} p_{L2} & 0 & 0 & 0 & 0 & 0\\
  \sigma_{L1} (1 - p_{L1}) & \sigma_{L2} (1 - p_{L2}) & \sigma_{L3} & 0 & 0 & 0 & 0 \\
  0 & 0 & 0 & \sigma_{J1} p_{J1} & 0 & 0 & 0 \\
  0 & 0 & 0 & \sigma_{J1} (1 - p_{J1}) & \sigma_{J2}  & \sigma_{A_R} & 0 \\
  0 & 0 & 0 & 0 & 0 & 0 & \sigma_{A_T} 
\end{bmatrix} \begin{bmatrix}
L_1 \\
L_2 \\
L_3 \\
J_1 \\
J_2 \\
A_R \\
A_T \\
\end{bmatrix}(t) 
$$

The parameters in this model are yearly survival probability $\sigma_{\cdot}$ (the subscript "$\cdot$" indicates a particular state variable), probability that a female frog reproduces in a given year $p_F$, number of eggs produced by a female frog in a year that successfully hatch $F$, probability of a first-year tadpole remaining as a tadpole $p_{L1}$, probability of a second-year tadpole remaining as a tadpole $p_{L2}$, and probability of a first-year juvenile remaining as a juvenile \$p\_{J1}\$.
First year juvenile survival and recruitment $\sigma_{J1}$ is the parameter that we think is most influenced environmental stochasticity.

@@

After parameterizing our model with CMR-estimated adult frog survival probabilities and other known vital rates ([@tbl-param_values]), we performed four analyses.
First, we compute the long-run growth rate $\lambda$ for each of our 12 translocated populations to determine if the populations were deterministically predicted to grow or decline in the long-run.
Second, we compute the elasticity of $\lambda$ to model parameters, to quantify how much changes in adult survival, for example, affected the long-run growth rate.
Third, we included demographic and environmental stochasticity in $\sigma_{J_1}$ in our model and simulated the 50-year viability (i.e., 1 - extinction probability) of populations given an introduction of 40 adult individuals into an unoccupied habitat.
Finally, we fit our model to our longest translocation trajectory to confirm that our model could reasonably reproduce the observed recovery trajectories of MYL frogs following reintroductions.
Additional details are provided in the SI Appendix.
Code to replicate the analyses can be found at <https://github.com/SNARL1/translocation>.

@@

![Population viability analysis of translocated MYL frogs quantified the long-run growth rate and extinction probability of frog populations: (A) Predicted long-run growth rate $\lambda$ for different values of yearly adult survival probability $\sigma_{A_R}$ and year 1 juvenile survival and recruitment probability $\sigma_{J_1}$, given the parameterized, deterministic model. Colored points show the predicted $\lambda$ values for the twelve translocated populations when year 1 juvenile survival probability is $\sigma_{J_1} = 0.09$ (indicated by the dashed line). The red line shows where $\lambda = 1$. Note that the point for 70413 is mostly hidden behind other points. (B) Predicted 50-year extinction probabilities of the 12 translocated populations, given demographic stochasticity, environmental variability in $\sigma_{J_1}$, and different mean values of \$\\sigma\_{J_1}\$. There are 6 lines at extinction probability = 1, 5 of which (70414--70619) are hidden beneath the line for 70505 when $\sigma_{J_1} < 0.10$. (C) 100 simulated trajectories (black lines) from the population viability model that most closely matched the observed abundance trajectory of adult amphibians at site 70550 (light orange).](figures/pop_viability_figures_for_manuscript.jpg){#fig-viability width="600"}

@@

We extracted yearly survival probabilities for translocated adults $\sigma_{A_T}$ and naturally recruited adults $\sigma_{A_R}$ from the CMR model used to estimate population-level parameters of translocated populations (see "Materials and Methods - Estimation of frog survival and abundance" in main paper).
Although we observed yearly variability in adult survival within a population, the magnitude of this variability was small compared to among-population variability ([@fig-translocation-survival]).
Thus, we did not include yearly within-population variability in adult survival in this analysis.
However, within a population there was substantial yearly variability in the successful recruitment of adults, greater than what we would expect from Poisson variability around a mean value.
Therefore, we allowed for yearly variability in the probability of year 1 juvenile survival and recruitment (additional details provided in "Estimating model parameters" below).
We also could have included environmental stochasticity in year 2 juvenile survival and recruitment \$\\sigma\_{J_2}\$, but our elasticity analysis showed that this parameter had little effect on host growth rate relative to $\sigma_{J_1}$

@@

We performed four analyses on our model.
First, we considered a deterministic version of our model with no yearly heterogeneity in year 1 juvenile survival and recruitment probability $\sigma_{J_1}$, and calculated the predicted long-run growth rate $\lambda$ of a population for different values of $\sigma_{A_R}$ and $\sigma_{J_1}$.
We then fixed $\sigma_{J_1} = 0.09$ and calculated the predicted growth rate of our 12 populations.

Second, we performed a local elasticity analysis on $\lambda$ with respect to parameters \$\\sigma\_{J_1}\$, $\sigma_{J_2}$, $\sigma_{A_R}$, and $F$ to determine how small changes in these parameters could influence the long-run deterministic growth rate of populations (@fig-viability-supp).

Third, we defined a version of the model with demographic and environmental stochasticity, where environmental stochasticity was represented by among-year variability in $\sigma_{J_1}$.
We used this model to simulate a one-time introduction of 40 translocated adult frogs.
We ran this simulation 1000 times for each population and computed the probability of a population becoming extinct after 50 years given the observed parameter values and environmental stochasticity in $\sigma_{J_1}$.
We varied the mean recruitment probability $\sigma_{J_1}$ from 0 and 0.25 and drew values of $\sigma_{J_1}$ each year from a beta distribution with a dispersion parameter of $\phi = 2$ (when $\sigma_{J_1} = 0.5$ and $\phi = 2$ the beta distribution is uniform between 0 and 1).
Using different values of $\phi$ does not qualitatively change the existence of distinct extinction dynamics between populations with $\sigma_{A_R} < 0.5$ and those with $\sigma_{A_R} > 0.5$.
However, increasing yearly variability in $\sigma_{J_1}$ increases extinction risk for all populations.
For example, if we set $\phi = 0.001$, such that in a given year essentially either all year 1 juveniles survive or all of them die, populations with $\sigma_{A_R} > 0.5$ need to have $\sigma_{J_1}$ greater than 0.2 to have a 50-year extinction probability of less 50%.
Because we do not pit tag juveniles, we do not have CMR estimates for $\sigma_{J_1}$ or $\phi$.
However, based on qualitative and semi-quantitative field observations over 25 years, a value of $\sigma_{J_1} = 0.25$ in the presence of Bd is probably a reasonable estimate for many populations.
Thus, we expect our model predictions to be conservative with regards to population recovery.

Finally, we assessed whether our stochastic model could reproduce observed trajectories of population recovery.
We focused on population 70550 because this was our longest CMR time series for a translocated population and because this population shows evidence of substantial post-translocation increases in adult abundance associated with population establishment and recovery.
We simulated our model for 16 years, repeating the simulation 50,000 times.
For each run and each year, we drew $\sigma_{J_1}$ from a uniform distribution between 0 and 1 (or equivalently a beta distribution with mean 0.5 and $\phi = 2$).
Using Approximate Bayesian Computing and rejection sampling [@kosmala2016], we identified the top 2% of trajectories (i.e., 1000 trajectories) that minimized the sum of squared errors between the observed and predicted data.
The yearly $\sigma_{J_1}$ values associated with these "best" trajectories represented an approximate posterior distribution [@beaumont2010].
Using these best fit trajectories, we assessed whether our model could qualitatively describe the patterns of recovery in the observed data for population 70550.

@@

![Sensitivity analysis of the stage-structured MYL frog model. Elasticity of $\lambda$ with changes in four parameters: $\sigma_{A_R}$ (yearly survival probability of naturally recruited adults), *F (*number of eggs produced by a female frog in a year that successfully hatch), $\sigma_{J_1}$ (yearly probability of survival of year 1 juveniles that also affects recruitment), and $\sigma_{J_2}$ (yearly probability of survival and recruitment of year 2 juveniles). Elasticity is calculated at the default parameter values for each population and $\sigma_{J_1}$ = 0.09.](figures/pop_viability_figures_for_supp.jpg){#fig-viability-supp width="450"}

@@

| **Parameter**                                                             | **Value**            | **Source**                                                                        |
|:---------------------------|:------------------|:-------------------------|
| $\sigma_{L_1}$, Yearly survival probability of year 1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{L_2}$, Yearly survival probability of year 2 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{L_3}$, Yearly survival probability of year 3 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{J_1}$, Yearly survival probability of year 1 juveniles           | Varies yearly        | Varies. Bounds estimated from field data, observations, natural history knowledge |
| $\sigma_{J_2}$, Yearly survival probability of year 2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from mark-recapture studies                                             |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from mark-recapture studies                                             |
| $p_{L_1}$, Probability of a year 1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations, natural history knowledge                |
| $p_{L_2}$, Probability of a year 2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations, natural history knowledge                |
| $p_{J_1}$, Probability of a year 1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, natural history knowledge                |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                                |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                                |
